Results

### 2021-08-30 Manuscript/Manuscript_Results.Rmd
Title change
results update
put info on the first query

---
title: "Manuscript"
date: "`r lubridate::today()`"
output:
  github_document:
    html_preview: false
---

@@

```{r session 1}
records_s1 <- import_data(session1_files$Records)

@@

@@

The final piece *AND ((antimicrobial resistance) OR (healthcare infection)* was added manually to better define the search domain, since the algorithm was trained on documents that were all more or less related to these topics.\
The generated query also provides a more nuanced understanding of the engine's internal classification logic, and this is helpful to spot possible biases in the model.

>>>>

---
title: "Results"
date: "`r lubridate::today()`"
output:
  github_document:
    html_preview: false
---

@@

```{r session 1}

first_query <- import_data('Session_journal.csv') %>% 
    filter(Session_ID == 'Session1') %>% 
    with(Query[1])

records_s1 <- import_data(session1_files$Records)

@@

The input search query was:\

*`r first_query`*

including results between 2010 and 2020 (included). The automatic search tools were used for MEDLINE, WOS and IEEE, while a manual search and importation was necessary for EMBASE and SCOPUS. The search was repeated manually also for MEDLINE, since, as reported in the methods, the web interface may return different results from the API.

@@

The final piece *AND ((antimicrobial resistance) OR (healthcare infection)* was added manually to better define the search domain, since the algorithm was trained on documents that were all more or less related to these topics.\
The generated query also provides a more nuanced understanding of the engine's internal classification logic, and this is helpful to spot possible biases in the model.\

The search was done with the same year filter and procedures of the first session.\
